---
title: "Movies Popularity"
author: "Ekin Kizildas, Aurora Sterpellone"
date: "2025-02-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# SCRAPING AND WORKING ON THE DATASET
## Necessary Libraries

```{r}
library(scrapex)
library(dotenv)
library(httr)
library(jsonlite)
library(furrr)
library(tidyverse)
library(future)
library(tibble)
library(dplyr)
library(fuzzyjoin)
library(rvest)
library(stringr)
library(tidyr)

```

## API SETUP

This R script fetches and processes movie data using The Movie Database (TMDb) API (https://developer.themoviedb.org/docs/getting-started). 

```{r}
#usethis::edit_r_environ()

api_key <- Sys.getenv("api_key")

```

## LET'S SCRAPE

This part sets up reproducible parallel processing to retrieve the top 50 movies for specified languages from 2000 to the current year. The script defines functions to fetch movie data and regional release dates for selected countries, handling API requests and responses efficiently. It uses parallel processing to speed up data retrieval and combines the results into data frames. Finally, it validates the data and saves the movie information with regional release dates to a CSV file, printing the dataset's dimensions and a preview of the data.

```{r}
set.seed(123)  # Ensures reproducibility
plan(multisession, workers = 4)  # Enable parallel processing


# Define time range
start_year <- 2000
end_year <- as.numeric(format(Sys.Date(), "%Y"))

# Define countries
countries <- c("US", "GB", "DE", "FR", "TR", "IN", "JP", "ES", "IT", "BR")

# Define selected languages
languages <- c("es", "fr", "de", "tr", "ja", "ru", "zh", "ko", "pt", "hi", "it")

### **STEP 1: Fetch Top 50 Movies Per Language**
fetch_movies_by_language <- function(lang) {
  movies_list <- list()

  for (page in 1:2) {  # Limit to first 2 pages (~50 movies per language)
    movie_url <- paste0("https://api.themoviedb.org/3/discover/movie?api_key=", api_key,
                        "&sort_by=popularity.desc",
                        "&primary_release_date.gte=", start_year, "-01-01",
                        "&primary_release_date.lte=", end_year, "-12-31",
                        "&vote_count.gte=500",
                        "&with_original_language=", lang,
                        "&page=", page)

    response <- tryCatch({
      GET(movie_url, timeout(10))
    }, error = function(e) NULL)

    Sys.sleep(runif(1, 1, 2))  # Short delay (1-2 sec) to avoid rate limits

    if (!is.null(response) && status_code(response) == 200) {
      movies <- fromJSON(content(response, "text", encoding = "UTF-8"))$results

      if (!is.null(movies) && length(movies) > 0) {
        movie_df <- tibble(
          movie_id = movies$id,
          title = movies$title,
          release_year = substr(movies$release_date, 1, 4),
          popularity = movies$popularity,
          original_language = movies$original_language,
          poster_path = paste0("https://image.tmdb.org/t/p/w500", movies$poster_path)
        )
        movies_list <- append(movies_list, list(movie_df))
      }
    }
  }

  if (length(movies_list) > 0) {
    return(bind_rows(movies_list))
  } else {
    return(NULL)
  }
}

# Fetch movies in parallel
all_movies <- future_map_dfr(languages, fetch_movies_by_language, .progress = TRUE, .options = furrr_options(seed = TRUE))

# Ensure data is not empty
if (nrow(all_movies) == 0) {
  stop("🚨 No movies were fetched! Check API key or language codes.")
}

### **STEP 2: Fetch Regional Release Dates**
fetch_regional_release_dates <- function(movie) {
  movie_id <- movie$movie_id
  title <- movie$title
  lang <- movie$original_language

  regional_release_dates <- future_map_dfr(countries, function(country) {
    release_dates_url <- paste0("https://api.themoviedb.org/3/movie/", movie_id,
                                "/release_dates?api_key=", api_key)

    response <- tryCatch({
      GET(release_dates_url, timeout(8))
    }, error = function(e) NULL)

    Sys.sleep(runif(1, 1, 2))  # Short delay to avoid rate limiting

    if (!is.null(response) && status_code(response) == 200) {
      release_dates_data <- fromJSON(content(response, "text", encoding = "UTF-8"))$results
      country_release_date <- release_dates_data[release_dates_data$iso_3166_1 == country, ]

      if (!is.null(country_release_date) && nrow(country_release_date) > 0) {
        return(tibble(
          movie_id = movie_id,
          title = title,
          language = lang,
          country = country,
          release_date = country_release_date$release_dates[[1]]$release_date
        ))
      }
    }
    return(NULL)
  }, .progress = TRUE, .options = furrr_options(seed = TRUE))

  return(regional_release_dates)
}

# Fetch regional release dates in parallel
all_movies_regional_release_dates <- future_map_dfr(
  split(all_movies, seq(nrow(all_movies))), 
  fetch_regional_release_dates, 
  .progress = TRUE, 
  .options = furrr_options(seed = TRUE)
)

# Ensure regional release data is not empty
if (nrow(all_movies_regional_release_dates) == 0) {
  stop("🚨 No regional release dates fetched! Check API key or country codes.")
}

# Save final dataset
write.csv(all_movies_regional_release_dates, "movies_with_regional_release_dates.csv", row.names = FALSE)

print(dim(all_movies_regional_release_dates))
head(all_movies_regional_release_dates)

```

```{r}
set.seed(123)
# Enable parallel processing (4 workers)
plan(multisession, workers = 4)

# ✅ Define time range
start_year <- 2000
end_year <- as.numeric(format(Sys.Date(), "%Y"))

# ✅ Define selected languages
languages <- c("es", "fr", "de", "tr", "ja", "ru", "zh", "ko", "pt", "hi", "it")

### **STEP 1: Fetch Top 50 Movies Per Language (Faster)**
fetch_movies_by_language <- function(lang) {
  movies_list <- list()

  for (page in 1:2) {  # ✅ Limit to first 2 pages (~50 movies per language)
    movie_url <- paste0("https://api.themoviedb.org/3/discover/movie?api_key=", api_key,
                        "&sort_by=popularity.desc",
                        "&primary_release_date.gte=", start_year, "-01-01",
                        "&primary_release_date.lte=", end_year, "-12-31",
                        "&vote_count.gte=500",
                        "&with_original_language=", lang,
                        "&page=", page)

    response <- tryCatch({
      GET(movie_url, timeout(10))
    }, error = function(e) NULL)

    Sys.sleep(runif(1, 1, 2))  # ✅ Shorter delay (1-2 sec)

    if (!is.null(response) && status_code(response) == 200) {
      movies <- fromJSON(content(response, "text", encoding = "UTF-8"))$results

      if (!is.null(movies) && length(movies) > 0) {
        movie_df <- tibble(
          movie_id = movies$id,
          title = movies$title,
          release_year = substr(movies$release_date, 1, 4),
          popularity = movies$popularity,
          original_language = movies$original_language,
          poster_path = paste0("https://image.tmdb.org/t/p/w500", movies$poster_path)
        )
        movies_list <- append(movies_list, list(movie_df))
      }
    }
  }

  if (length(movies_list) > 0) {
    return(bind_rows(movies_list))
  } else {
    return(NULL)
  }
}

# ✅ Fetch movies in parallel
all_movies <- future_map_dfr(languages, fetch_movies_by_language, .progress = TRUE, .options = furrr_options(seed = TRUE))

# ✅ Save movies dataset
write.csv(all_movies, "optimized_movies.csv", row.names = FALSE)

print(dim(all_movies))
head(all_movies)

```

### Join the 2 datasets

Here, we join the 2 datasets we have created from scraping TMDB.

```{r}
# Load necessary libraries
library(dplyr)

# Merge the datasets on the 'movie_id' column
merged_data <- all_movies %>%
  left_join(all_movies_regional_release_dates, by = "movie_id")

```

## SCRAPING AWARDS

### Scraping for the Academy Awards

```{r}
# Wikipedia page URL
oscar_url <- "https://en.wikipedia.org/wiki/List_of_Academy_Award%E2%80%93winning_films"

# Read the page
oscar_page <- read_html(oscar_url)

# Select the table that contains the Oscar-winning movies
oscar_movies <- oscar_page %>%
  html_nodes("table.wikitable") %>%
  .[[1]] %>%
  html_table(fill = TRUE)

# Show first few rows
print(head(oscar_movies))

# Rename columns for clarity
colnames(oscar_movies) <- c("film", "year", "awards_won", "nominations")

# Clean data and handle non-numeric values safely
oscar_movies_clean <- oscar_movies %>%
  mutate(
    year = as.numeric(str_extract(year, "\\d{4}")),  # Extract only the year
    awards_won = as.numeric(gsub("[^0-9]", "", awards_won)),  # Remove non-numeric characters
    nominations = as.numeric(gsub("[^0-9]", "", nominations))  # Remove non-numeric characters
  ) %>%
  drop_na()  # Remove rows with missing values

# Show cleaned dataset
print(head(oscar_movies_clean, 10))

# Save the cleaned data to a CSV file
write.csv(oscar_movies_clean, "oscar_winning_films.csv", row.names = FALSE)

```

### Scraping for Venice's Golden Lions

```{r} 
url <- "https://en.wikipedia.org/wiki/Golden_Lion"

page <- read_html(url)

tables <- page %>%
  html_nodes("table.wikitable")

golden_lion_table <- tables[[1]] %>%
  html_table(fill = TRUE)

print(colnames(golden_lion_table))

if (any(is.na(colnames(golden_lion_table))) | any(colnames(golden_lion_table) == "")) {
  colnames(golden_lion_table) <- c("Year", "Film", "Director", "Country")
}

golden_lion_clean <- golden_lion_table %>%
  rename(year = Year, film = `English Title`, director = Director, country = `Production Country`) %>%
  filter(!is.na(year) & year != "") %>%  # Boş satırları temizle
  mutate(
    year = as.numeric(str_extract(year, "\\d{4}")),  
    film = str_trim(film),  
    director = str_trim(director),  
    country = str_trim(country)  
  )

print(head(golden_lion_clean, 10))

write.csv(golden_lion_clean, "venice_film_festival_winners.csv", row.names = FALSE)

```

### Scraping for Cannes' Palme D'Or

```{r} 
# Wikipedia page URL for Palme d'Or winners
url <- "https://en.wikipedia.org/wiki/Palme_d%27Or"

# Read the page
page <- read_html(url)

# Get all tables from the page
tables <- page %>%
  html_nodes("table.wikitable")

# Extract tables 7, 8, and 9
table_7 <- tables[[7]] %>% html_table(fill = TRUE)
table_8 <- tables[[8]] %>% html_table(fill = TRUE)
table_9 <- tables[[9]] %>% html_table(fill = TRUE)

# Combine the tables into a single data frame
palme_dor_tables <- bind_rows(table_7, table_8, table_9)

# Check column names
print(colnames(palme_dor_tables))

# If column names are empty, assign new names
if (any(is.na(colnames(palme_dor_tables))) | any(colnames(palme_dor_tables) == "")) {
  colnames(palme_dor_tables) <- c("Year", "Film", "Director", "Country")
}

# Clean the data
palme_dor_clean <- palme_dor_tables %>%
  rename(year = Year, film = `English Title`, director = Director, country = `Production Country`) %>%
  filter(!is.na(year) & year != "") %>%  # Remove empty rows
  mutate(
    year = as.numeric(str_extract(year, "\\d{4}")),  # Extract year in numeric format
    film = str_trim(film),  # Trim film title
    director = str_trim(director),  # Trim director name
    country = str_trim(country)  # Trim country name
  )

# Display the cleaned data
print(head(palme_dor_clean, 10))

# Save the cleaned data to a CSV file
write.csv(palme_dor_clean, "cannes_film_festival_winners.csv", row.names = FALSE)

```

#### Merging the Awards Datasets

Here, we merge the different datasets we created by scraping for the different awards. We followed different steps:

1. rename columns

```{r}
# Load the datasets
cannes_winners <- palme_dor_clean
venice_winners <- golden_lion_clean
oscar_winners <- oscar_movies_clean

# Rename columns in cannes_winners
cannes_winners <- cannes_winners %>%
  rename(
    title = film,
    original_title = `Original Title`
  ) %>%
  select(year, title, original_title, director, country)

# Rename columns in venice_winners and drop the 'country' column
venice_winners <- venice_winners %>%
  rename(
    title = film,
    original_title = `Original Title`
  ) %>%
  select(-country)  # Drop the 'country' column

# Rename columns in oscar_winners
oscar_winners <- oscar_winners %>%
  rename(title = film)

```

2. binary indicators

```{r}
# Create binary indicator columns for each award

cannes_winners <- cannes_winners %>%
  mutate(palme_dor = 1) %>%
  select(title, original_title, year, director, country, palme_dor)

venice_winners <- venice_winners %>%
  mutate(golden_lion = 1) %>%
  select(title, original_title, year, director, golden_lion)

oscar_winners <- oscar_winners %>%
  mutate(academy_award = 1, academy_nominated = ifelse(nominations > 0, 1, 0)) %>%
  select(title, year, academy_award, academy_nominated)

# Merge the datasets
# First, merge Oscar winners with Cannes winners
merged_data_awards <- full_join(oscar_winners, cannes_winners, by = c("title", "year")) %>%
  mutate(
    academy_award = ifelse(is.na(academy_award), 0, academy_award),
    academy_nominated = ifelse(is.na(academy_nominated), 0, academy_nominated),
    palme_dor = ifelse(is.na(palme_dor), 0, palme_dor)
  )

# Next, merge the result with Venice winners
merged_data_awards <- full_join(merged_data_awards, venice_winners, by = c("title", "year")) %>%
  mutate(
    golden_lion = ifelse(is.na(golden_lion), 0, golden_lion)
  )

# Print the resulting dataset
print(merged_data_awards)

# Filter the dataset to include only movies from 2000 to 2025
merged_data_awards <- merged_data_awards %>%
  filter(year >= 2000 & year <= 2025)

```

3. delete original_title & director columns

```{r}
merged_data_awards <- merged_data_awards %>%
  select(-original_title.x, -original_title.y, -director.x, -director.y, -country)

```

4. dealing with NAs in academy_award - academy_nominated - palme_dor

```{r}
merged_data_awards <- merged_data_awards %>%
  mutate(across(c(academy_award, academy_nominated, palme_dor), ~ replace(., is.na(.), 0)))

```

5. Save everything

```{r}
# Save the resulting dataset to a CSV file
write.csv(merged_data_awards, "merged_awards_data.csv", row.names = FALSE)

```

## CREATE A UNIQUE DATASET

We merged all the datasets to create one single dataset

```{r}
movies_data <- all_movies
awards_data <- merged_data_awards

final_data <- left_join(movies_data, awards_data, by = "title")

final_data <- final_data %>%
  mutate(across(c(academy_award, academy_nominated, palme_dor, golden_lion), ~ replace(., is.na(.), 0)))

```

rename columns

```{r}
# Rename 'title.x' and 'title.y' to 'title' for consistency
merged_data <- merged_data %>%
  rename(title = title.x) %>%
  select(-title.y)  # Remove 'title.y' as it's redundant

# Merge the datasets on the 'title' column
final_data <- merged_data %>%
  left_join(merged_data_awards, by = "title")

# Deal with NAs in awards variables
final_data <- final_data %>%
  mutate(across(c(academy_award, academy_nominated, palme_dor, golden_lion), ~ replace(., is.na(.), 0)))

```

delete "year" column

```{r}
final_data <- final_data %>%
  select(- year)

```

## Export

```{r}
write.csv(final_data, "final_data.csv")

```

# ANALYSIS & VISUALIZATIONS

## Necessary Libraries

```{r}
library(tidyverse)
library(tidytext)  
library(ggwordcloud)  
library(dplyr)  
library(ggplot2)
library(stopwords)
library(igraph)
library(ggraph)
library(scales)
library(networkD3)
library(stats)
library(highcharter)
library(tidyr)
library(RColorBrewer)

```


## Visualization

In this section, we created some visualization to describe … ??

#### Number of Movies by Year

```{r}
final_data <- read.csv("final_data.csv")

# 1. Number of Movies by Year
ggplot(final_data, aes(x = as.factor(release_year))) +
  geom_bar(fill = "blue", alpha = 0.7) +
  labs(title = "Number of Movies by Year", x = "Release Year", y = "Movie Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### Movie Distribution by Country (Top 10 countries producing the most movies)

```{r}
# 2. Movie Distribution by Country (Top 10 countries producing the most movies)
top_countries <-final_data %>%
  count(country, sort = TRUE) %>%
  top_n(10, n)

ggplot(top_countries, aes(x = reorder(country, n), y = n)) +
  geom_bar(stat = "identity", fill = "red", alpha = 0.7) +
  coord_flip() +
  labs(title = "Top 10 Countries Producing the Most Movies", x = "Country", y = "Movie Count") +
  theme_minimal()

```

### Popularity Distribution

```{r}
# 3. Popularity Distribution
ggplot(final_data, aes(x = popularity)) +
  geom_histogram(bins = 20, fill = "green", color = "black", alpha = 0.7) +
  labs(title = "Popularity Distribution", x = "Popularity", y = "Movie Count") +
  theme_minimal()

```

### Language Distribution (Top 10 most used languages)

```{r}
# 5. Language Distribution (Top 10 most used languages)
top_languages <- final_data%>%
  count(language, sort = TRUE) %>%
  top_n(10, n)

ggplot(top_languages, aes(x = reorder(language, n), y = n)) +
  geom_bar(stat = "identity", fill = "purple", alpha = 0.7) +
  coord_flip() +
  labs(title = "Top 10 Most Used Languages", x = "Language", y = "Movie Count") +
  theme_minimal()
```

### Popularity vs. Awards

```{r}
# Calculate total awards
final_data <- final_data %>%
  mutate(total_awards = academy_award + academy_nominated + palme_dor + golden_lion)

# Scatter plot
ggplot(final_data, aes(x = popularity, y = total_awards)) +
  geom_point(alpha = 0.6, color = "purple") +
  geom_smooth(method = "lm", color = "red", se = FALSE) +  # Regression line
  labs(title = "Popularity vs. Awards", x = "Popularity", y = "Total Awards") +
  theme_minimal()

```

### Words in Movie Titles

```{r}
word_data <- final_data %>%
  filter(!is.na(title)) %>%
  unnest_tokens(word, title) %>%
  count(word, sort = TRUE) %>%
  filter(n > 5)  # Keep words appearing more than 5 times

# Remove stop words (English and other common words)
word_data <- word_data %>%
  filter(!word %in% stopwords("en"))  # Remove common English stop words

# Improved Word Cloud
ggplot(word_data, aes(label = word, size = n, color = n)) +
  geom_text_wordcloud() +
  scale_color_viridis_c() +
  labs(title = "Most Common Words in Movie Titles ") +
  theme_minimal()

```

### TO CHECK 

```{r}
df_pairs <- final_data %>%
  select(title, country) %>%  
  group_by(title) %>%
  summarise(country_pairs = if (n_distinct(country) > 1) {
    list(combn(unique(country), 2, simplify = FALSE))
  } else {
    list(NULL)
  }) %>%
  unnest(country_pairs) %>%
  filter(!is.null(country_pairs)) %>%
  unnest_wider(country_pairs, names_sep = "_") %>%
  rename(from = country_pairs_1, to = country_pairs_2) %>%
  count(from, to, name = "weight")

country_graph <- graph_from_data_frame(df_pairs, directed = FALSE)


print(country_graph)

```
#### MISSING THE TITLE

```{r}
# Veriyi hazırlayalım
nodes <- data.frame(name = unique(c(df_pairs$from, df_pairs$to)))
nodes$id <- 0:(nrow(nodes) - 1)

links <- df_pairs %>%
  left_join(nodes, by = c("from" = "name")) %>%
  rename(source = id) %>%
  left_join(nodes, by = c("to" = "name")) %>%
  rename(target = id) %>%
  mutate(value = weight)

forceNetwork(Links = as.data.frame(links), Nodes = as.data.frame(nodes), 
             Source = "source", Target = "target", 
             NodeID = "name", Value = "value", 
             Group = "name", opacity = 0.9, 
             zoom = TRUE, fontSize = 12)


```

### TITLE??

```{r}
V(country_graph)$degree <- degree(country_graph)

node_colors <- brewer.pal(n = 8, name = "Dark2")

ggraph(country_graph, layout = "fr") +  
  geom_edge_link(aes(edge_width = weight, alpha = weight), color = "gray") +  
  scale_edge_width(range = c(0.5, 5), trans = "log10") +  
  scale_edge_alpha(range = c(0.3, 1)) +  
  geom_node_point(aes(size = V(country_graph)$degree, color = as.factor(V(country_graph)$degree))) +  
  scale_color_manual(values = node_colors) +  
  geom_node_text(aes(label = name), repel = TRUE, size = 6, fontface = "bold") +  
  theme_void()

```

Looking at the visualization, we can see that some countries, like the United States (US), France (FR), and Germany (DE), have larger nodes. This indicates that they are key players in international co-productions, frequently working with multiple other nations. The thickness of the edges reveals which partnerships are the strongest. For example, if there is a thick line between US and FR, it means these two countries have collaborated on many films.

In contrast, some countries, like Brazil (BR) or Italy (IT), have smaller nodes, meaning they are involved in fewer co-productions. They might still play a role in international films but not as frequently as the major hubs. Additionally, some countries may have only a few connections, suggesting that they primarily produce films domestically rather than engaging in frequent international partnerships.


## Preparing the data

In this code, we prepare the data for visualizations by grouping the dataset by movie title and summarizing key attributes such as popularity, release dates, and awards. We then filter the data to identify the top 10 most popular movies based on their average popularity score. This process ensures that the data is structured and ready for creating insightful visualizations.

```{r}
# Assuming final_data is your dataset
# Group by movie title and summarize the data
grouped_data <- final_data %>%
  group_by(title) %>%
  summarise(
    movie_id = first(movie_id),
    release_year = first(release_year),
    popularity = mean(popularity, na.rm = TRUE),
    poster_path = first(poster_path),
    language = first(language),
    country = toString(unique(country)),  # Combine unique countries
    release_date = toString(unique(release_date)),  # Combine unique release dates
    academy_award = max(academy_award),
    academy_nominated = max(academy_nominated),
    palme_dor = max(palme_dor),
    golden_lion = max(golden_lion)
  ) %>%
  ungroup()

# Filter the top 10 most popular movies
top_10_movies <- grouped_data %>%
  arrange(desc(popularity)) %>%
  head(10)

```


## Awards Distribution

The provided code generates bar charts to visualize the distribution of awards among movies, using data from a dataset. For all movies, it sums up the counts of various awards and creates a bar plot to show the dominance of Academy Awards and nominations. Similarly, for the top 10 most popular movies, it highlights the prevalence of Academy recognition, while other prestigious awards like the Palme d'Or and Golden Lion are less represented.

### Awards Distribution for All Movies

```{r}
# Create a bar plot to show the distribution of different awards won by movies
awards_distribution <- final_data %>%
  select(academy_award, academy_nominated, palme_dor, golden_lion) %>%
  summarise_all(sum) %>%
  pivot_longer(cols = everything(), names_to = "Award", values_to = "Count")

highchart() %>%
  hc_chart(type = 'column') %>%
  hc_xAxis(categories = awards_distribution$Award) %>%
  hc_add_series(name = "Awards Count", data = awards_distribution$Count, color = "#1c9099") %>%
  hc_title(text = "Awards Distribution") %>%
  hc_subtitle(text = "All movies")
```

The first bar chart illustrates the distribution of various awards across all movies in the dataset. We can notice:

★ Academy Award and Academy Nominated: Both categories have the highest counts, indicating that a significant number of movies have either won or been nominated for Academy Awards. This suggests a strong representation of these movies in prestigious award ceremonies.

★ Palme d'Or and Golden Lion: These awards have much lower counts compared to the Academy-related categories. This indicates fewer movies in the dataset have received these awards, which are associated with the Cannes Film Festival (Palme d'Or) and the Venice Film Festival (Golden Lion).

### Awards Distribution for Top 10 Most Popular Movies

```{r}
# Create a bar plot to show the distribution of different awards won by movies
awards_distribution <- top_10_movies %>%
  select(academy_award, academy_nominated, palme_dor, golden_lion) %>%
  summarise_all(sum) %>%
  pivot_longer(cols = everything(), names_to = "Award", values_to = "Count")

highchart() %>%
  hc_chart(type = 'column') %>%
  hc_xAxis(categories = awards_distribution$Award) %>%
  hc_add_series(name = "Awards Count", data = awards_distribution$Count, color = "#8856a7") %>%
  hc_title(text = "Awards Distribution") %>%
  hc_subtitle(text = "Top 10 Most Popular Movies")

```

The second bar chart focuses on the top 10 most popular movies, showing a similar pattern:

★ Academy Award and Academy Nominated: These categories again dominate, with equal counts, suggesting that the most popular movies are also frequently recognized by the Academy.

★ Palme d'Or and Golden Lion: These awards are absent in the top 10 most popular movies, indicating that popularity, as measured here, does not necessarily correlate with winning these specific awards.


We notice that both charts highlight the prominence of Academy Awards and nominations in the dataset, while Palme d'Or and Golden Lion awards are less common. The top 10 most popular movies are particularly notable for their Academy recognition, but not for the other prestigious awards, suggesting a potential disparity between popularity and critical acclaim from international film festivals.


## Top Movies by Popularity

The code generates a bar and line chart to visualize the top 10 movies by popularity, highlighting various awards they have received. It uses the highchart function to create a column chart for popularity and overlays line charts to represent different awards, such as Academy Awards, nominations, Palme d'Or, and Golden Lion.

```{r}
# Create a bar plot to highlight the top 10 movies by popularity and show their awards
highchart() %>%
  hc_chart(type = 'column') %>%
  hc_xAxis(categories = top_10_movies$title) %>%
  hc_add_series(name = "Popularity", data = top_10_movies$popularity, color = "#dd1c77") %>%
  hc_add_series(name = "Academy Award", data = top_10_movies$academy_award, type = 'line', color = "darkgreen") %>%
  hc_add_series(name = "Academy Nominated", data = top_10_movies$academy_nominated, type = 'line', color = "#31a354") %>%
  hc_add_series(name = "Palme D'Or", data = top_10_movies$palme_dor, type = 'line', color = "#a1d99b") %>%
  hc_add_series(name = "Golden Lion", data = top_10_movies$golden_lion, type = 'line', color = "#e5f5e0") %>%
  hc_title(text = "Top Movies by Popularity and Awards") %>%
  hc_subtitle(text = "Highlighting Awards Won")

```

The graph illustrates the popularity of the top 10 movies with bars, while lines indicate the awards each movie has won. "I'm Still Here" stands out with the highest popularity, though it has minimal awards. Most movies show a consistent pattern of receiving Academy nominations, but few have won the Palme d'Or or Golden Lion, suggesting that popularity does not necessarily correlate with winning these prestigious awards.

## Popularity by release year

The code calculates the average popularity of movies for each release year and creates a line chart to visualize these trends over time. It groups the data by release year, computes the mean popularity, and uses the highchart function to plot the results, highlighting how movie popularity has evolved.

```{r}
# Calculate average popularity by release year
popularity_by_year <- grouped_data %>%
  group_by(release_year) %>%
  summarise(avg_popularity = mean(popularity, na.rm = TRUE))

# Create a line chart
highchart() %>%
  hc_chart(type = 'line') %>%
  hc_xAxis(title = list(text = "Release Year"), categories = popularity_by_year$release_year) %>%
  hc_add_series(name = "Average Popularity", data = popularity_by_year$avg_popularity, color = "#8856a7") %>%
  hc_title(text = "Average Movie Popularity by Release Year") %>%
  hc_subtitle(text = "Trends in Movie Popularity Over Time")


```

The graph shows fluctuations in movie popularity from 2000 to 2024, with a noticeable peak in 2024. This suggests a recent surge in popularity, possibly due to recent releases or increased interest in movies. Overall, the trend indicates variability in popularity over the years, with some periods of decline and recovery.



